I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-09 Paper/Paper_noProof.tex
background

@@

Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
denoting $\hat{\boldsymbol{z}}^{i}(n)={\boldsymbol{z}}^0$, we define inductively the weight vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
\begin{align*}
	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
	\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
\end{align*}

The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
$\boldsymbol{z}$ is called pre-activation values, 
and $\boldsymbol{z}^{(i)}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
Neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$. We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output.

@@

The verification problem is to determine whether the output of a neural network will be affected under small perturbations to the input. In formula, if we use a distance $d$, and if the $\boldsymbol{x}_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(\boldsymbol{x},\boldsymbol{x}_0)<\varepsilon\}$ where $\varepsilon$ is the parameter measuring the size of perturbation. And the problem will be \begin{align*}
	\forall \boldsymbol{x}\in\mathcal{D} \   f(\boldsymbol{x}) = f(\boldsymbol{x}_0).
\end{align*} In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
\end{align*}

>>>>

\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vb}{\boldsymbol{b}}

@@

Given an input vector $\boldsymbol{z}^0 \in \mathbb{R}^{d_0}$, 
denoting $\hat{\boldsymbol{z}}^{0}={\boldsymbol{z}}^0$, we define inductively the weight vector $\boldsymbol{z}^i$ at layer $1 \leq i \leq \ell$ with
\begin{align*}
	{\boldsymbol{z}}^{i} &= \boldsymbol{W}^i\cdot \hat{\boldsymbol{z}}^{(i-1)}+ \boldsymbol{b}^i\\
	\hat{\boldsymbol{z}}^{i} &= ReLU({\boldsymbol{z}}^i).
\end{align*}

The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
$\boldsymbol{z}$ is called pre-activation values, 
and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output. Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$. Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$
the weight of neuron $a$ when the the input is $\boldsymbol{x}$.

@@

\medskip

Similarly, for simplicity, we focus on local robustness for the verification problem, altough generalization to other problems pose no problem. 
Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input. In formula, if we use a distance $d$, and if the $\boldsymbol{x}_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(\boldsymbol{x},\boldsymbol{x}_0)<\varepsilon\}$ where $\varepsilon$ is the parameter measuring the size of perturbation. And the problem will be \begin{align*}
	\forall \boldsymbol{x}\in\mathcal{D} \   f(\boldsymbol{x}) = f(\boldsymbol{x}_0).
\end{align*} In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
\end{align*}
